\documentclass[11pt, letterpaper]{memoir}
\usepackage{HomeworkStyle}
\geometry{margin=0.75in}



\begin{document}

\begin{center}
	{\large Quiz 9.2 -- Molecular Orbital Theory: Diatomic Molecules}
\end{center}
{\large Name: \rule[-1mm]{4in}{.1pt}

\subsection*{Homonuclear Diatomics}

\ch{O2^{4+}} and \ch{N2^{2+}} have the same number of electrons, so you might expect them to have identical electronic structure

\noindent $\circ$ Draw the molecular orbital energy level diagram for these two molecules, filled with the proper number of electrons

\vspace{30em}
\noindent $\circ$ Give the bond order of both molecules

\vspace{5em}
\noindent $\circ$ Describe how both molecules might interact with a strong magnetic field

\newpage
\subsection*{Heteronuclear Diatomics}

Consider the molecule HF. Because of the much higher nuclear charge on F, the H$1s$ orbital actually aligns best energetically with the F$2p_z$ orbital, so they are the two which combine to form a molecular orbital. $\alpha_{H1s} = -7.2eV$, $\alpha_{F2p}=-10.4eV$, and $\beta_{H1s-F2p}=-1.0eV$

\noindent $\circ$ Calculate the energies of the two molecular orbitals, and draw an energy-level diagram which includes both the energies of the atomic orbitals and molecular orbitals. Remember that for heteronuclear diatomics we usually assume that the overlap integral $S=0$

\vspace{27em}
\noindent $\circ$ Calculate the coefficients for both MOs and sketch how they might look considering the unequal contributions from both atoms

\newpage
\pagestyle{empty}
\addtocounter{page}{-1}
\newgeometry{margin=1.25in}
\section*{\emph{Good Bones}}
\paragraph{By Maggie Smith}~
\begin{verse}
	Life is short, though I keep this from my children.\\
	Life is short, and I’ve shortened mine\\
	in a thousand delicious, ill-advised ways,\\
	a thousand deliciously ill-advised ways\\
	I’ll keep from my children. The world is at least\\
	fifty percent terrible, and that’s a conservative\\
	estimate, though I keep this from my children.\\
	For every bird there is a stone thrown at a bird.\\
	For every loved child, a child broken, bagged,\\
	sunk in a lake. Life is short and the world\\
	is at least half terrible, and for every kind\\
	stranger, there is one who would break you,\\
	though I keep this from my children. I am trying\\
	to sell them the world. Any decent realtor,\\
	walking you through a real shithole, chirps on\\
	about good bones: This place could be beautiful,\\
	right? You could make this place beautiful.
\end{verse}

\end{document}
